The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-18 paper/Analisis.tex
Corrected paragraph in Off-Center section

For the central and homogeneous source distributions we find
that observers at different directions do not present an angular 
dependency, in particular they would infer luminosities
different from the isotropical value only at levels $< 3\%$.

In the case of the Off-center model the 
%But with the set up of the off-center models
%where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
%located at $\mathrm{\theta = \pi/2}$ we do find and angular dependency for both  
%off-center distributions, this is shown in Fig. \ref{fig:OCflux}. The bold line  
%represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
%the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
%with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
%show exactly the same trend. We find a high dependency in the viewing angle
%in particular the flux at $\mathrm{\theta = \pi/2}$ is $\simeq 88\%$ stronger than 
%at $\mathrm{\theta = \pi/3}$ this have important consequences in observations when 
%galaxies are oriented in random directions which implies that off-center emission
%is not going to be observed in all the observed galaxies.

@@

The outgoing spectra for two different spheres located at $\pm 0.5R$ 
are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
the resulting profiles show more interesting morphologies than in the
$\pm 0.25R$ case.

There are two new morphological features that off-center emission in 
rotating galaxies produces. First in some of our models with specific 
values of velocity and optical depth an asymmetry in the peak heights 
is presented, those off-center spheres \textit{(put image reference)} 
located at the positive side of $\hat{\textbf{x}}$ in Fig.\ref{fig:OCspheres}
present a higher peak in the red-shifted part, while those spheres located
at the negative side of $\hat{\textbf{x}}$ present a higher blue shifted peak,
we found that the higher asymmetry is for model with $\tau=10^7, V=200 kms^{-1}$ 
where one peak is $20\%$ higher than the other.

>>>>

For the central and homogeneous source distributions we find
that for observers located at  $\theta = pi/2$ the
angular dependency represented by $\mu$ doesn't show a considerable
variation in particular the observer would infer luminosities 
different from the isotropical value only at levels $< 3\%$.

In the case of the Off-center model with the set up showed in 
Fig.\ref{fig:OCspheres} where the galaxy is rotating around the  
$\hat{\textbf{z}}$ axis and the observer is also located at 
$\mathrm{\theta = \pi/2}$. The first result we get is that 
the angular dependency is almost the same for all the models
with different $\tau_{H}$ and $V_{max}$. Both spheres located 
at $R = 0.25$ and $R = 0.5$ show variation in the flux just at
values $< 14 \%$ this results are shown in \ref{fig:OCflux}.

@@

The outgoing spectra for two different spheres located at $\pm 0.5R$ 
are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
the resulting profiles show new interesting morphologies than in the
$\pm 0.25R$ case.

There are two new morphological features that off-center emission in 
rotating galaxies produces. First in some of our models with specific 
values of velocity and optical depth an asymmetry in the peak heights 
is presented. Those off-center spheres located at the positive side of 
$\hat{\textbf{x}}$ (solid lines) in Fig.\ref{fig:OCspheres} have a slightly
shift to redder part of the spectra while those located at the negative 
side of $\hat{\textbf{x}}$ are shifted to the bluer part, the model in 
which this is most notorious is for $R = 0.25$, $V_{max} = 50$ and $\tau=10^{5}$.
